---
title: "flowLearn training/test data for IMPC"
output:
    pdf_document
---

This worksheet demonstrates the use of training and test data for the IMPC bone marrow panel. The
data is organized into one .rmd file per sample. Each file contains a list of gates with each gate
having densities (using different granularities), threshold values, and a list of booleans
indicating the events belonging to the gated population.

# Libraries and functions

```{r}
source("functions.R")
```

# Parameters

Granularities were calculated for $granularity \in \{8, 16, 32, 64, 128, 256, 512\}$ features

```{r}
# Granularity of the density, i.e. number of features
granularity <- "64"

# Population of interest
population <- "NOT(Plasma)"
```

# Loading data

One file per sample, meaning one file corresponds to one training vector.

```{r}
# Path to training files
dirName <- 'trainingFiles'
sampleName <- 'BM 8,2f,24,2f,15_L000096187_016.labelled'
sample <- readRDS(paste(dirName, '/', sampleName, '.rds', sep = ''))
```

# Accessing data

The loaded sample contains a list with a number of fields named by the gated population.

```{r}
# Print list of populations
print(names(sample))
```

Each list entry contains a object of class TrainingGate.

```{r}
print(class(sample[[population]]))
```

The slots are:

```{r}
print(slotNames("TrainingGate"))
```

- \texttt{parentName}: Name of the parent population

- \texttt{channelA}: Index of the first channel (A)

- \texttt{channelB}: Index of the second channel (B)

- \texttt{thresholdALow}: Low threshold of the channel A. The threshold might be \texttt{NaN}
  indicating that only one or no threshold was used for gating the population using this channel.

- \texttt{thresholdAHigh}: High threshold of the channel A. The threshold might be \texttt{NaN}
  indicating that only one or no threshold was used for gating the population using this channel.

- \texttt{thresholdBLow}: Low threshold of the channel B. The threshold might be \texttt{NaN}
  indicating that only one or no threshold was used for gating the population using this channel.

- \texttt{thresholdBHigh}: High threshold of the channel B. The threshold might be \texttt{NaN}
  indicating that only one or no threshold was used for gating the population using this channel.

- \texttt{negate}: TRUE if the population was negated, meaning that not the gated population is of interest
  but everything else

- \texttt{gateAssignments}: List of logicals with length = number of events, where each entry is TRUE if the
  event belongs to the population of interest

- \texttt{densitiesA}: A list with calculated densities for channel A for different granularities. Each entry
  is the returned value of Rs density function.

- \texttt{densitiesB}: A list with calculated densities for channel B for different granularities. Each entry
  is the returned value of Rs density function.

# Plotting densities and thresholds

I provided a convenience function for plotting the densities of channel A and B for one particular
gate. Have a look at this function to know how to use the different low and high threshold values.

```{r fig.height = 7}
plotGate(sample[[population]], granularity)
```

# Accessing density data

For each granularity, there is a density object containing different fields. The most important
fields are \texttt{x} and \texttt{y} describing the density distribution.

```{r}
x <- sample[[population]]@densitiesA[[granularity]]$x
y <- sample[[population]]@densitiesA[[granularity]]$y
```

